An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/intro.tex
config: intro

The downside of these approaches is that their learning approaches 
are limited to simplistic configuration errors, 
such as type errors and syntax errors, or they 
heavily rely on template-based inference~\cite{zhang14encore}. 
As we mentioned earlier, 
because configuration files are not written in a typed language 
with a fixed syntax,
type errors and syntax errors are relatively rare and easy to detect. 
However, many sophisticated configuration errors, 
which are difficult to template in practice, 
cannot be detected by this way. 
As an illustration of such an error consider the ordering errors, 
which happens when some entries are inserted in a wrong order. 
For example, if in a PHP configuration file 
an entry {\tt extension = mysql.so} appears 
before {\tt extension = recode.so},  
it would lead to a crash error, where the Apache server cannot start 
due to the segmentation fault error. The correct ordering 
should be {\tt extension = recode.so} before 
{\tt extension = mysql.so}~\cite{yin11anempirical}.
These types of errors cannot be detected by existing
learning efforts, 
since it is hard to build a corresponding template~\cite{xu15systems}: 
we would need to capture ordering relations of all the entries. 
Some of them can appear in an arbitrary ordering, 
and the resulting templates would be too large 
and not efficient for a practical use.

@@

Building such an automatic verification framework for
configuration files, nevertheless, requires addressing several challenges. 
First, for variables of one type 
we learn different rules than for variables of different types. 
For example, for integer variables $X$ and $Y$, 
we can learn that $X \leq Y$, while 
for strings we might want to learn a substring relation. We, therefore, first need to assign a type to every variable in a configuration file during the transformation phase.
However,
the type of a variable cannot always be fully determined 
from a single value. 
For example, an entry {\tt temp\_dir = 300} assigns to variable {\tt temp\_dir} either a directory named ``300'' or sets the size of that directory to 300 (an integer).
Some of existing type inference 
work would report this is an error, because {\tt temp\_dir} should be assigned
an integer~\cite{zhang14encore}. We address this problem by introducing the concept of
{\emph{probabilistic types}}.
Rather than assigning only one variable to a single type, 
we assign several types with their probability distributions. 
The entry in the above example might be assigned 
the following probabilistic type
{\tt \{temp\_dir, 300, [(File, 60\%), (Int, 40\%)]\}}.
Using the probabilistic types model,
we can generate a more accurate language model,
thus significantly improving our verification capabilities.

>>>>

The downside of these approaches is that their learning approaches 
are limited to simplistic configuration errors, 
such as type errors and syntax errors, or they 
heavily rely on template-based inference~\cite{zhang14encore}. 
%As we mentioned earlier, 
%because configuration files are not written in a typed language 
%with a fixed syntax,
%type errors and syntax errors are relatively rare and easy to detect. 
Many sophisticated configuration errors, 
which are difficult to template in practice, 
cannot be detected by this way. 
As an illustration of such an error, consider the ordering errors, 
which happens when some entries are inserted in a wrong order. 
For example, if in a PHP configuration file 
an entry {\tt extension = mysql.so} appears 
before {\tt extension = recode.so},  
it would lead to a crash error, where the Apache server cannot start 
due to the segmentation fault error. The correct ordering 
should be {\tt extension = recode.so} before 
{\tt extension = mysql.so}~\cite{yin11anempirical}.
These types of errors cannot be detected by existing
learning efforts, 
since it is hard to build a corresponding template~\cite{xu15systems}. 
%we would need to capture ordering relations of all the entries. 
%Some of them can appear in an arbitrary ordering, 
%and the resulting templates would be too large 
%and not efficient for a practical use.

@@

Building such an automatic verification framework for
configuration files, nevertheless, requires addressing several challenges. 
%First, for variables of one type 
%we learn different rules than for variables of different types. 
%For example, for integer variables $X$ and $Y$, 
%we can learn that $X \leq Y$, while 
%for strings we might want to learn a substring relation. 
First, we need to assign a type to every variable in a configuration file during the transformation phase.
However,
the type of a variable cannot always be fully determined 
from a single value. 
For example, an entry {\tt temp\_dir = 300} assigns to variable {\tt temp\_dir} either a directory named ``300'' or sets the size of that directory to 300 (an integer).
Some of existing type inference 
work would report this is an error, because {\tt temp\_dir} should be assigned
an integer~\cite{zhang14encore}. We address this problem by introducing the concept of
{\emph{probabilistic types}}.
Rather than assigning only one variable to a single type, 
we assign several types with their probability distributions. 
The entry in the above example might be assigned 
the following probabilistic type
{\tt \{temp\_dir, 300, [(File, 60\%), (Int, 40\%)]\}}.
Using the probabilistic types model,
we can generate a more accurate language model,
thus significantly improving our verification capabilities.
